---
title: "Medical Education(MEED)"
output: 
  flexdashboard::flex_dashboard:
    css: style.css
    social: menu
    source_code: embed
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)

`%>%` <- magrittr::`%>%`
### Pulling most recent data from Github
italy_region <- readr::read_csv("https://raw.githubusercontent.com/RamiKrispin/covid19Italy/master/csv/italy_region.csv")
italy_region$date <- as.Date(italy_region$date)


italy_total <- readr::read_csv("https://raw.githubusercontent.com/RamiKrispin/covid19Italy/master/csv/italy_total.csv")
italy_total$date <- as.Date(italy_total$date)


#------------------ Parameters ------------------
# Set colors: https://www.w3.org/TR/css-color-3/#svg-color
tested_color <- "purple"
positive_color <- RColorBrewer::brewer.pal(9, "PuRd")[7]
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
# death_color <- "#660708"
death_color <- "red"
intensive_care_color <- "#ba181b"
h_symptoms_color <- "#e5383b"
home_conf_color <- "#FDBBBC"


italy_total_last <- italy_total %>% dplyr::filter(date == max(date))


italy_total <- italy_total %>% 
  dplyr::arrange(date) %>%
  dplyr::mutate(tested_daily = total_tests - dplyr::lag(total_tests, n = 1),
                daily_new_cases = c(NA,diff(italy_total$cumulative_cases))) %>%
  dplyr::mutate(new_cases_smooth = (daily_new_cases +
                                    dplyr::lag(daily_new_cases, n = 1) +
                                    dplyr::lag(daily_new_cases, n = 2) +
                                    dplyr::lag(daily_new_cases, n = 3) +
                                    dplyr::lag(daily_new_cases, n = 4)) / 5)

italy_total$tested_daily[1] <- italy_total$total_tests[1]

```

Summary
=======================================================================
Column { data-width=150 }
-----------------------------------------------------------------------
### tested {.value-box}
```{r}
valueBox(value = paste(format(italy_total_last$total_tests, big.mark = ","), "", sep = " "), 
         caption = "Total Tested Cases", 
         icon = "fas fa-user-md", 
         color = tested_color)
```

### Positive Cases {.value-box}

```{r}
valueBox(value = paste(format(italy_total_last$cumulative_cases, big.mark = ","), "", sep = " "), 
         caption = "Total Positive Cases", 
         icon = "far fa-plus-square", 
         color = positive_color)
```



Column { data-width=425 }
-----------------------------------------------------------------------

### Daily New Cases

```{r daily_new}
plotly::plot_ly(data = italy_total,
                x = ~ date,
                y = ~ c(NA,diff(italy_total$cumulative_cases)),
                type = "scatter",
                mode = "markers",
                name = "Positive Cases") %>%
  plotly::add_lines(x = ~ date, 
                    y = ~ new_cases_smooth,
                    line = list(color = "#fb5607", width = 3),
                    name = "Trend Line") %>%
  plotly::layout(title = "",
                 legend = list(x = 0.03, y = 0.95),
                 yaxis = list(title = "Number of Cases"),
                 xaxis = list(title = "Using 5 days trailing moving average to calculate the trend line"),
                 hovermode = "compare")
  
```


Column { data-width=425 }
-----------------------------------------------------------------------

### Daily Death Cases

```{r}
plotly::plot_ly(data = italy_total,
                x = ~ date,
                y = ~ c(NA,diff(italy_total$death)),
                type = "scatter",
                mode = "line",
                name = "Death Cases",
                 line = list(color = death_color)) %>%
  plotly::layout(title = "",
                 yaxis = list(title = "Number of Death"),
                 xaxis = list(title ="")) %>%
  plotly::add_annotations(text =  paste("The daily number of cases is", 
                                        "calculated by taking the diff",
                                        "of the cumulative cases.",
                                        "Some anomalies may exist",
                                        "(negative count or unexplained",
                                        "spikes) is in the raw data.",
                                        sep = "<br>"),
                          align = "center",
                          y = 0.35,
                          x = as.Date("2020-08-15"),
                          # axref="x",
                          # ayref='y',
                          xref = "x",
                          yref = "paper",
                          showarrow = TRUE,
                          arrowhead = 1,
                          ax = -10,
                          ay = -90)
```


### Distribution between Recovery and Death

```{r}
plotly::plot_ly(data = italy_total,
                x = ~ date,
                y = ~ recovered, 
                name = 'Recovered', 
                fillcolor = recovered_color,
                type = 'scatter',
                mode = 'none', 
                stackgroup = 'one', groupnorm = 'percent') %>%
  plotly::add_trace( y = ~ death, 
                     name = "Death",
                     fillcolor = death_color) %>%
  plotly::layout(title = "",
                 legend = list(x = 0.75, y = 0.05),
                 ticksuffix = "%",
                 yaxis = list(title = "Recoverd / Death Dist (%)", 
                              showgrid = FALSE,
                              hoverformat = ".2f",
                              ticksuffix = "%"),
                 xaxis = list(title = "Source: Italy Department of Civil Protection", showgrid = FALSE),
                 hovermode = "compared")
```



About
=======================================================================

**Data**

The input data for this dashboard are the XXX. The data and dashboard are updated regularly. 

**Data source**

The raw data for XXX is pulled from XXX

**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package for the plots and [mapview](https://r-spatial.github.io/mapview/) package for the map 
* Data manipulation - [dplyr](https://dplyr.tidyverse.org/), and [tidyr](https://tidyr.tidyverse.org/)
* Tables - the [DT](https://rstudio.github.io/DT/) package
